%------------------------------------------------------
% Cover Letter -- NGUYEN KHAC BAO
% Target: Intern AI/ML/Data Engineer @ Nexlab Technology
% Compile: pdflatex CoverLetter_Nguyen_Khac_Bao_Nexlab.tex
%------------------------------------------------------

\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,top=0.85in,bottom=0.85in,left=1in,right=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{microtype}

\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    pdfborder={0 0 0}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{7pt}
\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Nguyen Khac Bao}\\
Ho Chi Minh City, Vietnam\\
\href{mailto:nguyenkhacbaowork564@gmail.com}{nguyenkhacbaowork564@gmail.com} \,\textbullet\,
(+84) 039 586 4429 \,\textbullet\,
\href{https://github.com/NguyenKhacBao564}{github.com/NguyenKhacBao564}
\end{flushleft}

\vspace{4pt}
\hfill May 11, 2026

\vspace{8pt}

\begin{flushleft}
\textbf{Hiring Team}\\
Nexlab Technology\\
Ho Chi Minh City, Vietnam
\end{flushleft}

\vspace{4pt}

\textbf{Re: Application for Intern AI/ML/Data Engineer}

\vspace{8pt}

Dear Hiring Team at Nexlab Technology,

I am writing to apply for the Intern AI/ML/Data Engineer position. As an Information Technology student with a strong interest in RAG systems, LLM integration, and data pipelines, I am interested in Nexlab's work around AI agents for data analysis, automated reporting, and the modern data stack on Google Cloud.

Instead of only experimenting with models in notebooks, I focus on building small but complete AI systems. Recently, I developed a Vietnamese Legal RAG Chatbot, where I built a FastAPI backend, integrated Qdrant vector retrieval, designed an agent-style RAG workflow with LlamaIndex ReAct tools, and connected Gemini/OpenAI-compatible endpoints for chatbot responses. I also fine-tuned Llama-3.1-8B with PEFT/LoRA on Vietnamese legal QA data using Vast.ai GPU.

Beyond the chatbot, my FallGuard and Traffic Violation projects helped me practice data engineering fundamentals: raw data ingestion, CSV/JSON metadata tracking, data quality checks, annotation review, dataset splitting, and reproducible export workflows. These experiences align with the role's focus on clean data flow for AI models and dashboards.

I understand that Nexlab's stack includes tools such as BigQuery, Cloud Storage, Vertex AI, Looker, and Power BI. While my current hands-on cloud experience is still basic, mainly with Google Cloud Run microservices, AWS EC2, Docker, and Vast.ai GPU, I am comfortable self-learning from technical documentation and applying new tools in real projects.

I am available for a full-time internship and would be glad to contribute to RAG chatbot development, ETL/ELT pipelines, SQL-based data processing, and AI reporting workflows at Nexlab. Thank you for your time and consideration.

\vspace{10pt}

Sincerely,

\vspace{16pt}

\textbf{Nguyen Khac Bao}

\end{document}
