%------------------------------------------------------
% Harvard-style one-page resume -- NGUYEN KHAC BAO
% Target: Intern AI/ML/Data Engineer @ Nexlab Technology
% Compile: pdflatex CV_Nguyen_Khac_Bao_Nexlab_AI_ML_Data_Engineer_Intern.tex
%------------------------------------------------------

\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,top=0.42in,bottom=0.42in,left=0.55in,right=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{microtype}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    pdfborder={0 0 0}
}

\titleformat{\section}
    {\normalfont\large\bfseries}
    {}
    {0em}
    {}
    [\vspace{1pt}\titlerule]

\titlespacing*{\section}{0pt}{5pt}{2pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}
\sloppy

\newenvironment{cvitems}{%
    \begin{itemize}[leftmargin=1.25em,itemsep=0pt,topsep=1pt,parsep=0pt]
}{%
    \end{itemize}
}

\newcommand{\entryhead}[2]{%
    \noindent\textbf{#1}\hfill #2\\[-2pt]
}

\newcommand{\entrysub}[1]{%
    \noindent\textit{#1}\\[-1pt]
}

\begin{document}
\fontsize{9.25}{10.25}\selectfont

\begin{center}
    {\Large\textbf{NGUYEN KHAC BAO}}\\[-1pt]
    Intern AI/ML/Data Engineer\\[2pt]
    Ho Chi Minh City, Vietnam
    \,\textbar\,
    \href{mailto:nguyenkhacbaowork564@gmail.com}{nguyenkhacbaowork564@gmail.com}
    \,\textbar\,
    (+84) 039 586 4429
    \,\textbar\,
    \href{https://github.com/NguyenKhacBao564}{github.com/NguyenKhacBao564}
\end{center}

\section{CAREER OBJECTIVE}
AI/ML/Data Engineer Intern candidate with hands-on experience building RAG chatbots, LLM integrations, and reliable data pipelines. Interested in applying Python, SQL, and cloud-based microservices to build AI agents for data analysis, reporting, and business automation.

\section{EDUCATION}
\entryhead{Posts and Telecommunications Institute of Technology (PTIT)}{2022 -- 2027}
\entrysub{Bachelor of Information Technology}
Relevant Coursework: Machine Learning, Deep Learning, Database Systems, Computer Vision.

\section{TECHNICAL SKILLS}
\textbf{Programming Languages:} Python, SQL (joins, CTEs, basic window functions), Bash\\
\textbf{AI / LLMs:} RAG pipelines, LlamaIndex ReAct, Embeddings/Vector DBs, Prompt Engineering, PEFT/LoRA, Gemini/OpenAI-compatible APIs\\
\textbf{Data Engineering:} Pandas, JSONL/CSV processing, ETL/ELT basics, data preprocessing, data quality checks\\
\textbf{Backend / Tools:} FastAPI, Docker, Qdrant, Git/GitHub, Linux, Streamlit\\
\textbf{Basic Cloud \& Messaging:} Google Cloud Run (microservices), AWS EC2, Vast.ai (GPU), RabbitMQ

\section{LANGUAGES}
\entryhead{TOEIC: 610/990}{2026}
\entryhead{English: Technical reading proficiency}{}
Able to read official documentation, research papers, model cards, API references, and engineering articles in English.

\section{PROJECTS}
\entryhead{Vietnamese Legal RAG Chatbot}{2026}
\entrysub{Personal Project \textbar\ Technology: Python, FastAPI, Qdrant, LlamaIndex, Celery, Valkey, MariaDB, PEFT/LoRA, Gemini API \textbar\ Source: \href{https://github.com/NguyenKhacBao564/legal_RaG_Chatbot_VietNamese-System}{GitHub}}
\begin{cvitems}
    \item Built an end-to-end Vietnamese legal assistant with FastAPI, Streamlit, asynchronous task handling, conversation storage, Qdrant vector retrieval, and OpenAI-compatible LLM endpoints.
    \item Designed an agent-style RAG workflow to route queries between legal retrieval, LlamaIndex ReAct tools, web-search handling, and chat fallback.
    \item Implemented a data import and indexing pipeline from JSONL legal QA records into Qdrant, with hybrid retrieval, query expansion, reranking, and legal-context prompting.
    \item Fine-tuned Llama-3.1-8B-Instruct with PEFT/LoRA on Vietnamese legal QA data using Vast.ai GPU; integrated Gemini/local LLM APIs for chatbot responses.
    \item Dockerized the multi-service system and added safe repository rules to avoid committing API keys, datasets, logs, and model artifacts.
\end{cvitems}

\entryhead{FallGuard Labeling Tool -- Dataset Assistant}{2026}
\entrysub{Personal Project \textbar\ Technology: Python, Streamlit, OpenCV, Pandas, YOLO-Pose, CSV metadata \textbar\ Source: \href{https://github.com/NguyenKhacBao564/autofall-labeler-tool}{GitHub}}
\begin{cvitems}
    \item Built a dataset assistant for fall-detection image/video data: raw import, frame extraction, metadata generation, auto-label initialization, human review, QA checks, split, and export.
    \item Designed CSV-based source-of-truth records for metadata, annotations, keypoints, and annotation events to keep data review and export reproducible.
    \item Integrated YOLO-Pose and a Streamlit review UI for label correction, uncertain/excluded samples, pose quality review, and manual keypoint editing.
\end{cvitems}

\entryhead{Traffic Violation Detection \& License Plate Recognition}{2026}
\entrysub{Personal Project \textbar\ Technology: Python, OpenCV, YOLO, ByteTrack, HyperLPR3, NumPy, Shapely, JSON \textbar\ Source: \href{https://github.com/NguyenKhacBao564/Traffic-Violation-Detection-and-License-Plate-Recognition}{GitHub}}
\begin{cvitems}
    \item Built a fixed-camera traffic video pipeline for vehicle detection, tracking, traffic-light state estimation, stop-line violation logic, plate detection, OCR, and structured evidence generation.
    \item Fine-tuned a YOLO-based license plate detector on a compact CCPD2019 subset of 8,598 images, achieving 0.989 precision, 0.998 recall, and 0.994 mAP50 on validation.
    \item Implemented dataset QA checks for broken files, YOLO bbox validity, negative samples, OCR crop availability, duplicate review, low-light images, heavy blur, and small plates.
\end{cvitems}

\section{ACTIVITIES}
\entryhead{AI Research Group -- University Club}{2025 -- Present}
\entrysub{Member}
Discussed Machine Learning, RAG/LLM applications, Computer Vision, and AI system development.

\end{document}
