%------------------------------------------------------
% Harvard-style one-page resume -- NGUYEN KHAC BAO
% Target: Fullstack AI Integration Intern @ FPT Telecom
% Compile: pdflatex CV_Nguyen_Khac_Bao_FPT_Fullstack_AI_Integration_Intern.tex
%------------------------------------------------------

\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,top=0.38in,bottom=0.38in,left=0.52in,right=0.52in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{microtype}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    pdfborder={0 0 0}
}

\titleformat{\section}
    {\normalfont\large\bfseries}
    {}
    {0em}
    {}
    [\vspace{1pt}\titlerule]

\titlespacing*{\section}{0pt}{4pt}{2pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}
\sloppy

\newenvironment{cvitems}{%
    \begin{itemize}[leftmargin=1.2em,itemsep=0pt,topsep=1pt,parsep=0pt]
}{%
    \end{itemize}
}

\newcommand{\entryhead}[2]{%
    \noindent\textbf{#1}\hfill #2\\[-2pt]
}

\newcommand{\entrysub}[1]{%
    \noindent\textit{#1}\\[-1pt]
}

\begin{document}
\fontsize{9.05}{10.0}\selectfont

\begin{center}
    {\Large\textbf{NGUYEN KHAC BAO}}\\[-1pt]
    Fullstack AI Integration Intern\\[2pt]
    Ho Chi Minh City, Vietnam
    \,\textbar\,
    \href{mailto:nguyenkhacbaowork564@gmail.com}{nguyenkhacbaowork564@gmail.com}
    \,\textbar\,
    (+84) 039 586 4429
    \,\textbar\,
    \href{https://github.com/NguyenKhacBao564}{github.com/NguyenKhacBao564}
\end{center}

\section{CAREER OBJECTIVE}
AI integration intern candidate focused on turning AI models into usable products through backend APIs, RAG pipelines, vector databases, Docker, and cloud deployment. Hands-on with FastAPI, Streamlit, Gemini API, Qdrant Cloud, Cloud SQL, and Cloud Run for deployable AI demos.

\section{EDUCATION}
\entryhead{Posts and Telecommunications Institute of Technology (PTIT)}{2022 -- 2027}
\entrysub{Bachelor of Information Technology}
Relevant Coursework: Machine Learning, Deep Learning, Computer Vision.

\section{TECHNICAL SKILLS}
\textbf{AI Integration:} RAG pipelines, Gemini API, embeddings, prompt engineering, OpenAI-compatible APIs, LLM endpoint integration\\
\textbf{Backend / Cloud:} FastAPI, REST API, WebSocket, Docker, Google Cloud Run, Cloud SQL, Secret Manager, AWS EC2, Vast.ai GPU\\
\textbf{Databases:} Qdrant Cloud, MySQL/Cloud SQL, SQL basics, JSON/CSV data processing\\
\textbf{Frontend:} Streamlit, browser webcam demo, basic HTML/JavaScript\\
\textbf{ML / CV:} PyTorch, YOLOv8n, OpenCV, OCR, multi-object tracking, dataset QA\\
\textbf{Tools:} Git/GitHub, Linux, Cloud Build, Artifact Registry

\section{LANGUAGES}
Vietnamese: Native \textbar\ English: Technical reading proficiency for documentation, model cards, API references, and engineering articles.

\section{PROJECTS}
\entryhead{Vietnamese Legal RAG Chatbot}{2026}
\entrysub{Personal Project \textbar\ Python, FastAPI, Streamlit, Gemini API, Qdrant Cloud, Cloud SQL, Docker, Google Cloud Run \textbar\ Source: \href{https://github.com/NguyenKhacBao564/legal_RaG_Chatbot_VietNamese-System}{GitHub}}
\begin{cvitems}
    \item Built a cloud-ready fullstack RAG product demo with a Streamlit frontend and FastAPI backend deployed as separate Google Cloud Run services.
    \item Integrated Gemini as the default LLM and embedding provider; indexed the full 32,980-record Vietnamese legal QA dataset into Qdrant Cloud for retrieval-based answers.
    \item Used Cloud SQL/MySQL for chat history and environment-based configuration with Secret Manager for API keys and database credentials.
    \item Designed optional extensions for async document indexing with Celery/Redis-compatible broker and fine-tuned Vietnamese legal LLM serving through an OpenAI-compatible endpoint.
\end{cvitems}

\entryhead{Real-Time Face Mask Compliance Detection System}{2026}
\entrysub{Personal Project \textbar\ Python, FastAPI, WebSocket, YOLOv8n, OpenCV, Docker, Google Cloud Run \textbar\ Source: \href{https://github.com/NguyenKhacBao564/Real-Time-Face-Mask-Compliance-Detection-System}{GitHub}}
\begin{cvitems}
    \item Built and deployed an AI inference service with FastAPI REST + WebSocket endpoints and a browser webcam frontend running over Cloud Run HTTPS/WSS.
    \item Containerized the service for Cloud Run and logged warm endpoint latency around 151 ms for REST and 127 ms for WSS in the demo environment.
    \item Trained a YOLOv8n 3-class mask model on PWMFD converted from VOC to YOLO format: 9,205 images, 18,528 labeled instances, 0.970 mAP@50 validation.
\end{cvitems}

\entryhead{Traffic Violation Detection \& License Plate Recognition}{2026}
\entrysub{Personal Project \textbar\ Python, OpenCV, Ultralytics YOLO, ByteTrack, HyperLPR3, JSON \textbar\ Source: \href{https://github.com/NguyenKhacBao564/Traffic-Violation-Detection-and-License-Plate-Recognition}{GitHub}}
\begin{cvitems}
    \item Built an AI video analytics pipeline for vehicle detection/tracking, traffic-light state estimation, stop-line event logic, plate OCR, and JSON evidence bundles.
    \item Prepared a compact CCPD2019 plate dataset with annotation parsing, YOLO bbox conversion, train/val/test split, negative samples, OCR crops, and QA reports.
    \item Fine-tuned a YOLO plate detector on 8,598 images, achieving 0.989 precision, 0.998 recall, and 0.994 mAP50 on validation.
\end{cvitems}

\entryhead{Autofall Labeler Tool}{2026}
\entrysub{Additional Project \textbar\ Python, Streamlit, OpenCV, YOLO-Pose, Pandas \textbar\ Source: \href{https://github.com/NguyenKhacBao564/autofall-labeler-tool}{GitHub}}
\begin{cvitems}
    \item Built a human-in-the-loop dataset assistant with Streamlit review UI, metadata/annotation management, YOLO-Pose keypoints, QA reports, and reviewed-only export.
    \item Designed CSV-based source-of-truth records for annotations, metadata, keypoints, and review events to handle noisy CCTV data and reproducible dataset versioning.
    \item Achieved 90.2\% coarse fall/non-fall agreement on a reviewed benchmark while identifying exact action-label accuracy as a limitation of weak temporal modeling.
\end{cvitems}

\section{ACTIVITIES}
\entryhead{AI Research Group -- University Club}{2025 -- Present}
\entrysub{Member}
Discussed Machine Learning, Deep Learning, Computer Vision, and AI application development.

\end{document}
