%------------------------------------------------------
% Harvard-style Resume -- NGUYEN KHAC BAO
% Target: AI Engineer Intern @ Gameloft (dataset focus)
% Compile: pdflatex CV_Nguyen_Khac_Bao_Gameloft.tex
%          or upload to https://www.overleaf.com
%------------------------------------------------------

\documentclass[10pt, a4paper]{article}

%--- Packages ---
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, top=0.5in, bottom=0.5in, left=0.6in, right=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{microtype}

%--- Hyperlink style ---
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    pdfborder={0 0 0}
}

%--- Harvard section style: bold label + full-width rule beneath ---
\titleformat{\section}
    {\normalfont\normalsize\bfseries}
    {}
    {0em}
    {}
    [\vspace{1pt}\titlerule]

\titlespacing*{\section}{0pt}{6pt}{2pt}

%--- Helpers ---
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

%--- Tight bullet list ---
\newenvironment{cvitems}{%
    \begin{itemize}[leftmargin=1.4em, itemsep=0pt, topsep=1pt, parsep=0pt]
}{%
    \end{itemize}
}

%--- Entry header: left-aligned title, right-aligned date ---
\newcommand{\entryhead}[2]{%
    \noindent\textbf{#1}\hfill\textbf{#2}\\[-2pt]
}

%--- Sub-line (organisation / role) ---
\newcommand{\entrysub}[1]{%
    \noindent\textit{#1}\\[1pt]
}

%======================================================
\begin{document}

%---------- HEADER ----------
\begin{center}
    {\LARGE\textbf{NGUYEN KHAC BAO}}\\[5pt]
    Ho Chi Minh City, Vietnam
    \,\textbullet\,
    \href{mailto:nguyenkhacbaowork564@gmail.com}{nguyenkhacbaowork564@gmail.com}
    \,\textbullet\,
    (+84) 039 586 4429
    \,\textbullet\,
    \href{https://github.com/NguyenKhacBao564}{github.com/NguyenKhacBao564}
\end{center}

\vspace{4pt}

%---------- EDUCATION ----------
\section{Education}

\entryhead{Posts and Telecommunications Institute of Technology (PTIT)}{Ho Chi Minh City, Vietnam}
\entrysub{Bachelor of Information Technology \hfill 2022 -- Present}
Relevant Coursework: Machine Learning, Deep Learning, Computer Vision

%---------- SKILLS ----------
\section{Skills \& Technologies}

\noindent
\textbf{Data \& Annotation:} YOLO/VOC labeling, 13-point keypoint annotation, multi-source dataset merging, class normalization, train/val/test splitting, dataset audit (distribution, malformed labels, duplicates, blur/dark flags), metadata \& QA reports, version snapshots.\\
\textbf{Programming:} Python (NumPy, Pandas, Streamlit, PyYAML), C/C++ (basic).\\
\textbf{CV Frameworks:} PyTorch, Ultralytics YOLOv8/v11 (detection + pose), OpenCV, ByteTrack, EasyOCR, PaddleOCR.\\
\textbf{Cloud:} AWS (SageMaker, Lambda, S3), Google Cloud (Compute Engine, Cloud Storage, Vertex AI, Cloud Run).\\
\textbf{Tools:} Git/GitHub, Docker, Linux, Vast.ai, Jupyter, FastAPI, WebSocket.\\
\textbf{CV Tasks:} Object Detection, Pose Estimation, Video Analytics, Multi-object Tracking, Image Classification.\\
\textbf{Languages:} Vietnamese (native), English (technical reading proficiency).

%---------- PROJECTS ----------
\section{Projects}

%--- Project 1: FallGuard ---
\entryhead{FallGuard Labeling Tool --- Computer Vision Dataset Assistant}{2026}
\entrysub{Python, Streamlit, OpenCV, YOLO-Pose, Pandas \,\textbullet\,
  \href{https://github.com/NguyenKhacBao564}{GitHub Repository}}
\begin{cvitems}
    \item End-to-end dataset assistant: image/video ingestion, metadata tracking, auto pose-label generation, human review, QA reports, reviewed-only export.
    \item Streamlit review UI with bounding boxes, 13 keypoints, confidence scores, label correction, uncertain/exclude actions, manual keypoint editing for human-in-the-loop QA.
    \item Processed 5 videos into \textbf{656 reviewed frames}; versioned annotations, keypoint CSVs, event logs, QA reports, and validation snapshots.
\end{cvitems}

\vspace{3pt}

%--- Project 2: Face Mask ---
\entryhead{Real-Time Face Mask Compliance Detection System}{2026}
\entrysub{Python, YOLOv8n, OpenCV, Vast.ai \,\textbullet\,
  \href{https://github.com/NguyenKhacBao564/Real-Time-Face-Mask-Compliance-Detection-System}{GitHub Repository}}
\begin{cvitems}
    \item Converted PWMFD VOC$\rightarrow$YOLO: \textbf{9,205 images}, \textbf{18,528 face instances} with class mapping, split validation, empty-label handling, SHA-1 reproducible naming.
    \item Generated dataset audit reports: per-split counts, per-class distribution, malformed-line detection to enforce data quality before training.
    \item Trained on Vast.ai: validation \textbf{mAP@50 0.970}, \textbf{mAP@50:95 0.749}; documented limited \textit{incorrect\_mask} sample size and per-class recall impact.
    \item Collected real-world test capture metadata (mask subtype, lighting, occlusion, blur, reflection) for structured edge-case analysis.
    \item Planned dataset extension: hand-occlusion subclasses (e.g., \textit{correct\_mask\_hand\_covered}, \textit{incorrect\_mask\_hand\_covered}, \textit{no\_mask\_hand\_covered}) to handle real-world camera scenarios where users partially obscure their face by hand.
\end{cvitems}

\vspace{3pt}

%--- Project 3: Traffic ---
\entryhead{Traffic Violation Detection \& License Plate Recognition}{2026}
\entrysub{Python, YOLO, OpenCV, ByteTrack, OCR \,\textbullet\,
  \href{https://github.com/NguyenKhacBao564}{GitHub Repository}}
\begin{cvitems}
    \item Fixed-camera video pipeline: vehicle detection/tracking (ByteTrack), traffic-light ROI state, stop-line crossing logic, violation events, plate OCR.
    \item Prepared CCPD subset of \textbf{8,598 images}: YOLO plate labels, OCR crops, train/val/test splits, negative samples, manifest metadata.
    \item Audit artefacts flagging missing files, invalid YOLO boxes, duplicates, dark/blur/small-plate samples, and contact sheets for human QA.
\end{cvitems}

%---------- ACTIVITIES ----------
\section{Activities}

\entryhead{AI Research Group --- University Club}{Ho Chi Minh City, Vietnam}
\entrysub{Member \hfill 2024 -- Present}
\begin{cvitems}
    \item Discussions and literature reviews on Machine Learning and Computer Vision (object detection, data augmentation).
\end{cvitems}

\end{document}
